Viscous Erosion in Porous Media

### 2018-04-05 docs/methods/erosion_methods.tex
NM

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
\label{table:arangle}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% npts = 1024

@@

The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Intriguingly, erosion appears to remove material preferentially from these sights, as the narrow spacing between neighboring bodies expands rather quickly. For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4. Moreover, the bodies tend to develop flat faces at the points of near contact, leading to the appearance of straight channels between bodies. Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Once formed, these channels persist until the bodies have nearly vanished. Notice that by the final frame, body 4 has vanished completely, and the simulation handles this event without difficulty.

@@

>>>>

Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to smaller-scale structures and patterns \cite{}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay), along with small-scale biological structures such as biofilms. Motivated by these small-scale applications, this work focuses on developing numerical methods to simulate the erosion of solid material in Stokes flow.

Recent work on high-Reynolds number erosion has recognized the importance of shape-flow feedback

%% ORIGINAL %%%

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{The long-time aspect ratio and opening-angle measurements for three...
} 
\vspace{0.3 pc}
\label{table:arangle}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% npts = 1024

@@

The initial configuration in  Fig.~\ref{fig:06bodies} was selected to have several points at which the bodies nearly contact one another, for example between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Intriguingly, erosion appears to remove material preferentially from these sights, as the narrow spacing between neighboring bodies expands rather quickly. For example, the spacing between bodies 1 \& 2 is initially quite small, but by the second frame, is comparable to the spacing between bodies 3 \& 4. Moreover, the bodies tend to develop flat faces at these points of near contact, leading to the appearance of straight channels between bodies. Straight channels can be seen, for example, between bodies 1 \& 2, 3 \& 5, and 5 \& 6. Once formed, these channels persist until the bodies have nearly vanished. Notice that by the final frame, body 4 has vanished completely, and the simulation handles this event without difficulty.

@@

Look back at Fig. 1 and notice similar features: channelization, sort-of polygonal bodies, etc.
